KeysarMouseTracking.csv

### 2020-12-19 analysis/cogSci_analysis.Rmd
fix paths

```{r}
setwd('~/Repos/keysar_replication/experiment1/data/')
preMouseDExp1 = read.csv('mouse/fullSampleMouse.csv')
preErrorDExp1 = read.csv('error/fullSampleError.csv')
preMessageDExp1 = read.csv('message/fullSampleMessage.csv')

setwd('~/Repos/keysar_replication/experiment2/data/')
preMouseDExp2 = read.csv('mouse/exp2Mouse.csv')
preErrorDExp2 = read.csv('error/exp2Error.csv')
preMessageDExp2 = read.csv('message/exp2Message.csv')
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(binom)
```

@@

```{r}
library(boot)
library(irr)
turkerRatings <- read.csv("../normingExperiment/data/keysarNorming-trials.csv")
relevantProperties <- c("objectSet", "label")

criticalMessagesExp1 <- read.csv("../experiment1/data/processedLabelsExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../experiment2/data/processedLabelsExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

g <- (ggplot(Exp2ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point(aes(color = experiment), size = 2)
  + geom_errorbarh(aes(xmax = fitnessUpper, xmin = fitnessLower,
                       color = experiment), 
                  height = 0.01, alpha = .5)
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower,
                     color = experiment), 
                width = 0.05, alpha = .5)
  + geom_smooth(method = "lm",colour="black")
  + theme_few(base_size = 16)
  + theme(aspect.ratio=1)
  + ylab("Error rate")
  + xlab("Distractor fitness / target fitness"))
g
ggsave("~/Repos/keysar_replication/writing/cogsci-revision/images/itemWiseFitness.pdf")
```

@@

# Shoudln't worry too much about convergence errors: appear to be false positives
# https://groups.google.com/forum/#!topic/predicts_project/gVfnVxCSYog

# gg <- mmRes2@optinfo$derivs$grad
# hh <- mmRes2@optinfo$derivs$Hessian
# vv <- sqrt(diag(solve(hh/2)))
# print(summary(abs(gg*vv)))
# 
# relgrad <- with(mmRes2@optinfo$derivs,solve(Hessian,gradient))
# print(max(abs(relgrad)))

@@

# Create input for BDA

Create the informativities csv

```{r}
rbind(read_csv('../data/exp1SpeakerLabels.csv') %>% mutate(exp = 'scripted'),
      read_csv('../data/exp2SpeakerLabels.csv') %>% mutate(exp = 'unscripted')) %>%
  mutate(label = str_replace_all(label, fixed(' '), '')) %>%
  mutate(label = str_replace_all(label, "[[:punct:]]", "")) %>% 
  mutate(label = str_to_lower(label, locale = "en")) %>%
  write_csv(path = '../modeling/bdaInput/speakerData.csv')
```

>>>>

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(binom)

preMouseDExp1 = read.csv('../data/exp1Mouse.csv')
preErrorDExp1 = read.csv('../data/exp1Error.csv')
preMessageDExp1 = read.csv('../data/exp1Message.csv')

preMouseDExp2 = read.csv('../data/exp2Mouse.csv')
preErrorDExp2 = read.csv('../data/exp2Error.csv')
preMessageDExp2 = read.csv('../data/exp2Message.csv')
```

@@

```{r}
library(boot)
library(irr)
turkerRatings <- read.csv("../data/informativities.csv")
relevantProperties <- c("objectSet", "label")

criticalMessagesExp1 <- read.csv("../data/Exp1SpeakerLabels.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../data/Exp2SpeakerLabels.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

g <- (ggplot(Exp2ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point(aes(color = experiment), size = 2)
  + geom_errorbarh(aes(xmax = fitnessUpper, xmin = fitnessLower,
                       color = experiment), 
                  height = 0.01, alpha = .5)
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower,
                     color = experiment), 
                width = 0.05, alpha = .5)
  + geom_smooth(method = "lm",colour="black")
  + theme_few(base_size = 16)
  + theme(aspect.ratio=1)
  + ylab("Error rate")
  + xlab("Distractor fitness / target fitness"))
g
ggsave("../../writing/cogsci-revision/images/itemWiseFitness.pdf")
```

@@

@@
